Fractional Types

### 2013-02-24 frac.tex
_

>>>>

\roshan{In the above the, when we say that the terms of {{Pi}} are
  proofs that certain ``shapes of values'' are isomorphic, it is
  misleading. In {{langRev}}, the value {{left ()}} may or may not be
  isomorphic to the value {{right ()}} or {{left ()}} itself, or any
  other value of our choice. In particular the actual syntactic
  structure of the value has nothing to do with values being
  isomorphic. Values are just place-holders for the situations that
  their type represents. Their shapes have no intrinsic content. }

\roshan{Further, this is not to say that we may not be able to use the
  syntactic structure of a value for some purpose.  The prime use for
  such a thing might be, for example, to define a notion of distance
  between values -- such that values live in a metric space. Time and
  time again, we have felt the need for developing such an idea. Such
  a thing doesn't exist for the scope of this paper however. }
